The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types

### 2023-05-31 final/paper/main.tex

\title{The Accuracy of KNN, SVM, Bayes classifier, SVDD, neural network with DBSCAN, k-means, NN-chain for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types}

@@

\section*{Abstract}
Nowadays, using machine to give an early diagnosis of a cancer type is widely studied. 
In this paper, based on the gene-expression dataset on Synapse.org, we compare the performance of machine 
learning techniques, including data preprocessing, e.g., Principal components analysis (PCA), Autoencoder 
(AE), classification, e.g., k-nearest neighbors (KNN), support vector machine (SVM), neural network (NN), 
Support Vector Data Description (SVDD), naive Bayes classifier; 
and clustering for dealing with unknown types, e.g., k-means, density-based spatial clustering of 
applications with noise (DBSCAN) and nearest-neighbor chain (NN-chain).

@@

\bf{naive Bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian 
theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds. 
And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most 
likely outcome according to the conditional probability it just recorded.

@@

  In the other hand, KNN performs extraordinarily. In arrhythmia dataset, KNN with k-means in raw data gets 53.1646\% 
  accuracy, which is the highest accuracy comparing to others methods. And in gene expression cancer RNA-Seq dataset, 
  KNN with k-means in PCA data gets 94.8795\%. And KNN with DBSCAN performs well too. This method shows similar performance 
  in these two datasets, which also gets 94.5783\% in gene expression cancer RNA-Seq dataset PCA data.

@@

\section{Conclusion}
In this study, we present a framework of algorithm to deal with the dataset containing 
out-of-knowledge data. And with in this algorithm, multiple major machine learning 
techniques are used, e.g., for preprocess, PCA, AE, normalization; for classification, 
KNN, SVM, SVDD, NN, Bayes classifier, as for clustering, DBSCAN, k-means, NN-chain. Among the various 
combinations, PCA + KNN + k-means performs outstanding in gene expression cancer RNA-Seq 
dataset, and raw data + KNN + k-means performs the best in arrhythmia dataset. Accidently, 
SVM performs bad in these two dataset. The main cause is the defect of the multi-classification 
SVMs design, which make some SVMs hard to separate the target types. However, by customize 
the kernel for each SVM, the problem may ease. In the same time, the increasing number of 
parameters can be fine-tuned by metaheuristic algorithms, e.g., simulated annealing, genetic 
algorithm, etc. We will develope a refinement design on multi-classification SVMs, to enhance 
the accuracy on these datasets.

\section{Contribution}
\begin{itemize}
  \item Hsieh Cheng-Han: KNN, SVM, DBSCAN, paper, ppt
  \item Hsu Ting-Hao: 
  \item Sun Shih-Yu: SVM, k-means, paper
  \item Lu Che-Yuan: naive Bayes classifier
  \item Huang Chia-Yen: naive Bayes classifier, paper, poster
\end{itemize}

>>>>

\title{The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types}

@@

\section*{Abstract}
Nowadays, using machine to give an early diagnosis of a cancer type is widely studied. 
In this paper, based on the gene-expression dataset on Synapse.org, we compare the performance of machine 
learning techniques, including data preprocessing, e.g., Principal components analysis (PCA), Autoencoder 
(AE), classification, e.g., k-nearest neighbors (KNN), support vector machine (SVM), neural network (NN), 
and clustering for dealing with unknown types, e.g., k-means, density-based spatial clustering of 
applications with noise (DBSCAN).

@@

\bf{naive bayes classifier}: \rm{naive Bayes classifier} as its name suggest, is a machine learning method base on Bayesian 
theorem, this model will statistic each data and find all conditional probability of each event occurring if each outcome holds. 
And finally when it is asked to predict the result, the model will evaluate the data which requist provide and find the most 
likely outcome according to the conditional probability it just recorded.

@@

  On the other hand, KNN performs extraordinarily. In arrhythmia dataset, KNN with k-means in raw data gets 53.1646\% 
  accuracy, which is the highest accuracy comparing to others methods. And in gene expression cancer RNA-Seq dataset, 
  KNN with k-means in PCA data gets 94.8795\%. And KNN with DBSCAN performs well too. This method shows similar performance 
  in these two datasets, which also gets 94.5783\% in gene expression cancer RNA-Seq dataset PCA data.

  For the SVDD + NN with NN-chain, the performance is not as good as KNN, since SVDD cannot be trained with data augmented by 
  interpolation. The hypersphere that defined by SVDD includes all data points in the test dataset, which makes 
  clustering impossible. Therefore, though NN classifying achieves 100\% correctness on the known types, 
  the accuracy of SVDD + NN with NN-chain can only reach 64.45\% in gene expression cancer RNA-Seq dataset.

@@

\section{Conclusion}
In this study, we present a framework of algorithm to deal with the dataset containing 
out-of-knowledge data. And with in this algorithm, multiple major machine learning 
techniques are used, e.g., for preprocess, PCA, AE, normalization; for classification, 
KNN, SVM, SVDD, NN, as for clustering, DBSCAN, k-means, NN-chain. Among the various 
combinations, PCA + KNN + k-means performs outstanding in gene expression cancer RNA-Seq 
dataset, and raw data + KNN + k-means performs the best in arrhythmia dataset. Accidently, 
SVM performs bad in these two dataset. The main cause is the defect of the multi-classification 
SVMs design, which make some SVMs hard to separate the target types. However, by customize 
the kernel for each SVM, the problem may ease. In the same time, the increasing number of 
parameters can be fine-tuned by metaheuristic algorithms, e.g., simulated annealing, genetic 
algorithm, etc. We will develope a refinement design on multi-classification SVMs, to enhance 
the accuracy on these datasets. Another issue is SVDD, in 32 dimension PCA data, it can not 
separate the known and unkonwn types well. The reason behind is that in a lower dimension, 
the distance between known and unknown types are so close that SVDD can not separate them. 
If reduce the dataset to a relatively larger dimension, the problem may be solved.

\section{Contribution}
\begin{itemize}
  \item Hsieh Cheng-Han: KNN, SVM, DBSCAN, paper, ppt
  \item Hsu Ting-Hao: NN, SVDD, NN-Chain, paper, ppt
  \item Sun Shih-Yu: SVM, k-means, paper
  \item Lu Che-Yuan: naive Bayes classifier
  \item Huang Chia-Yen: naive Bayes classifier, paper, poster
\end{itemize}
